Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-08-04 Manuscript/MPESubmission/Revision/TEM_revised_manuscript.tex
error in highlighting (fixed)

\subsubsection{Missing data for fossil taxa ($M_{F}$)}
When the overall proportion of data for the fossil taxa ($M_{F}$) decreases, this also reduces the probability of morphological characters for fossil taxa overlapping with the ones for living taxa.
This can lead to difficulties for the placement of certain taxa in the tree.
It is important, however, to note that even though the number of displaced wildcard taxa increases (i.e. decrease of Normalised Triplets metric) with increasing missing data in this parameter, clade conservation (i.e. Normalised Robinson-Foulds metric) is still relatively good (mode = 0.72) when the proportion of missing data is high ($M_{F}$ = 75\%).
\hl{These results are in agreement with \cite{manosphylogeny2007} where as few as 16 characters where sufficient for correctly assigning ``artificial fossils'' to their ``correct'' clade.}

>>>>

\subsubsection{Missing data for fossil taxa ($M_{F}$)}
When the overall proportion of data for the fossil taxa ($M_{F}$) decreases, this also reduces the probability of morphological characters for fossil taxa overlapping with the ones for living taxa.
This can lead to difficulties for the placement of certain taxa in the tree.
It is important, however, to note that even though the number of displaced wildcard taxa increases (i.e. decrease of Normalised Triplets metric) with increasing missing data in this parameter, clade conservation (i.e. Normalised Robinson-Foulds metric) is still relatively good (mode = 0.72) when the proportion of missing data is high ($M_{F}$ = 75\%).
\hl{These results are in agreement with }\cite{manosphylogeny2007}\hl{ where as few as 16 characters where sufficient for correctly assigning ``artificial fossils'' to their ``correct'' clade.}
